Time delay estimation in unresolved lensed quasars

### 2020-12-26 paper/aa-package/paper.tex
intro

The paper is structured as follows: Sec. \ref{sec:MC} describes the Monte Carlo (MC) simulations we performed....

train a one-dimensional Convolutional Neural Network (CNN) to map non-resolved double-lensed quasar images into the corresponding time-delay. Starting from open-source real data \cite{CosmograilData} of resolved quasar light curves, we combine them into a single time series to mimic the real situation in which the quasar images are not resolved. Then, we feed the so-obtained time series into a GP-based algorithm, which artificially generates new realistic non-resolved quasar light curves along with their corresponding time-delays. Preliminary experiments based on data of quasars HE0435 and HS2209 demonstrate the effectiveness of the proposed method.

>>>>

The paper is structured as follows: Sec. \ref{sec:MC} describes the Monte Carlo (MC) simulations we performed.... Sec 3...
